Verifying Demonstrations

### 2017-08-23 conclusions.tex
Fixes some warnings from Syntastic

        \pause

@@

\begin{frame}
  \begin{question}
    \begin{itemize}
      \item How to avoid Sybil?
      \item Government can sign as many certificates as they like using their 
        national ID systems.
      \item Tie to something unique: phone, phone subscription?
      \item Register twice?
    \end{itemize}
  \end{question}

  \begin{question}
    Can we piggyback on existing \acp{PKI}?
    E.g.~\cite{Cinderella}.
  \end{question}

@@

  \mode<presentation>{
  \begin{remark}
    Without anonymous submission we don't get vote privacy, thus no receipt 
    freeness either.
  \end{remark}
  }
\end{frame}

>>>>

        \pause{}

@@

\begin{frame}
  \begin{question}
    How to solve Sybil, can we piggyback on existing \acp{PKI}?
    E.g.~\cite{Cinderella}.
  \end{question}

  \begin{question}
    Government can sign as many certificates as they like using their national 
    ID systems.
    How to deal with this?
  \end{question}

  \begin{question}
    Tie to something unique: phone, phone subscription?
    Register twice?
  \end{question}

@@

  \mode<presentation>{%
  \begin{remark}
    Without anonymous submission we don't get vote privacy, thus no receipt 
    freeness either.
  \end{remark}
  }
\end{frame}
